Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-04 1_manuscript/itt-emotion.tex
Made files to send to correction service 5707 words and 7729 words

\title{Cross-culture differences in tourists faced with Japanese hospitality: A text mining and natural language processing study of satisfaction and dissatisfaction factors in Chinese and Western cultures}

% Fold 1
  % Fold 2
    % Fold 3
      % Fold 4
        \titlerunning{Cross-culture differences in tourists faced with Japanese hospitality: A text ...}

@@

  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought in a global perspective in recent years, most tourist behavior studies were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes of a hotel like service or be more concerned with hard attributes like location and facilities? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists. The latter were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  Japan has been known historically for its hospitality being the highest grade. The spirit of Japanese hospitality is celebrated around the world in a single Japanese word: \textit{Omotenashi}. With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}. Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context? Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.

  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009} with a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China. Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing. From that, the number of researchers interested in this phenomenon has been increasing as well. \cite[][]{sun2017}. With these and other multicultural tourist populations, the tourist market is more and more diverse. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied. Hotel management, therefore, needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  However, a great majority of tourist behavior analysis has been performed with Western subjects and a gap in knowledge and discussion existed until the recent decades. Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few that compare Asian to western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples, which, while valid, can have its limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.

@@

  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}. With this data, we can confirm existing theories about their differences in behavior and perform an exploration of the data to discover factors that could have been overlooked in the past. To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel. We then perform a statistical extraction of the topics that concerns the customers of each population the most.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges. We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as relating to physicial aspects and environmental aspects, such as the facilities of the hotel, the location of the hotel, infrastructure and real estate nearby. In contrast, soft attributes are the non-physical attributes of the hotel related to services, staff or management.

  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose. The short scope of those studies means that cultural and language differences often cannot be observed in a single study.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}. This is permeating into every kind of business with customer interaction in Japan, where a simple convenience shop could express all of these standards of hospitality and service, which aren't exclusive to hotels.

    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer. However, in many cases, other factors such as proximity to a convenience store, or transport availability, or perhaps room quality might be more critical to a customer.  In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly, but rather consider it as a cultural factor that influences all businesses in Japan and observe the customers evaluations regarding service and hospitality factors in general, which can be compared to other places and business practice in the world. In summary, our study considers the influence of the cultural aspect of \textit{omotenashi}, while only studying the evaluations of service, hospitality and staff behavior factors that are universal to all hotels in any country.

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer, as well as the order in which they prioritize them.

@@

    In this study, however, we study not overall customer satisfaction, but the satisfaction and dissatisfaction that stem from individual specific expectations, be they conscious or unconscious. For example, if a customer has a conscious  expectation of a comfortable bed and a wide shower, and it is realized during their visit, they will be satisfied with this matter. However if that same customer had a conscious expectation of a comfortable sleep but there were loud noises at night, that is a different aspect that they can be dissatisfied with, regardless of the satisfaction towards the bed. Then, the same customer might have packed their own toiletries, thinking that the amenities might not include those, and then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. While this definition of satisfaction and our current method does not allow us to examine overall customer satisfaction, it will allow us to examine the factors that a hotel can revise individually, and how they are perceived by a population as a whole. In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different aspects of a service. In our study, therefore, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. Dissatisfaction, on the other hand, is the emotional response to the lack of a realization, or an under-performance of these conscious or unconscious expectations towards specific aspects of a service.

    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. The use of the Likert scale leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}. This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction. However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.

    Previous research has also focused more on soft attributes that are controllable by the hotel managers and staff, i.e., hotel services, staff behavior, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors uncontrollable by the hotel staff can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, as well as the integration of the hotel with tours available nearby, among other factors.

@@

    % We further want to analyze how the differently priced hotels differ in results:

    % \begin{rsq}
    % \label{rsq:price}
    % How do Chinese and Western customers' satisfaction and dissatisfaction change across different price ranges?
    % \end{rsq}

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused greatly on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior. Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of studies on Chinese tourism. This increase in research on Chinese tourist behavior resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies specifically comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer the hotel health facilities while the Asian tourists were more inclined to enjoy the Karaoke facilities of hotels, and both groups tend to have high expectations about the overall facilities. Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty. In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and an increase in knowledge as a common motivator.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000, and that they are not Chinese specific, but study Asian people in general. Meanwhile, the current Chinese economy boom is making an increase in the influx of tourists of this nation. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves, making the analysis unique in the exploring of their behavior in comparison with Western tourists, as well as studying them in the specific environment of high-level hospitality in Japan and observing hard factors that are not considered in most other studies.

@@

    % Universal behavior
    Other studies, perhaps recognizing that samples from Western industrialized countries are not representative, have gone further and studied people from many countries in their samples, and performed a more universal and holistic (not cross-culture) analysis. \cite{choi2001}, for example, analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants. As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries. The general satisfaction score was noticed to be different in those countries. However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed. As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.

@@

    % Chinese behavior
    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. Different researchers have found that Chinese tourist populations have several specific attributes. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities. \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism when compared with other international tourists. Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall. However, the younger generations seem to do so less than their older counterparts.

@@

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its top rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent. The number of samples in other text-mining studies is also smaller to ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Machine Learning
    The algorithm used for sentiment analysis in our study is called a Support Vector Machine. It is a form of supervised machine learning used for binary classification. This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically. Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task. Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template. Machine learning can also be unsupervised, where without any pre-labeled data. In this latter case, the machine will analyze the structure and patters on the data and perform a task based on its own conclusions. Our study calls for a supervised machine since text analysis can be intricate. Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels. Consequently, we teach the machine through previously labeled text samples.

    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand. Machine learning methods focus on predicting new data based on known properties and patterns of the given data. Data mining, on the other hand, is discovering new information and new properties of the data. Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction, and using these to label the rest of the data. We are not exploring new patterns in the sentiment data. However, we are using sentiment predictions for knowledge discovery in our database. Thus our study is a data mining experiment based on machine learning.

>>>>

\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}

% Fold 1
  % Fold 2
    % Fold 3
      % Fold 4
        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}

@@

  The Japanese spirit of hospitality and service \textit{Omotenashi} is known worldwide for its excellence. Recent years show a steady increase in international tourists coming to Japan. Chinese tourists, especially, have been steadily increasing. However, before the shift that has brought a global perspective in recent years, most tourist behavior studies were biased for the Western world. Previous research shows that different cultural backgrounds result in different expectations and, arguably, different satisfaction factors. Knowing this, a cross-cultural study of differences between Chinese and Western cultures after the current boom in the Chinese economy in the high standard Japanese hospitality environment is fascinating. Will the top-grade hospitality of Japan influence both populations equally, or will their cultural differences set them apart? Will they be satisfied with the soft attributes like service or be more concerned with hard attributes like location and facilities? We bring light to these questions and the differences in each population's satisfaction and dissatisfaction factors in different price ranges. Taking advantage of Web 2.0, we applied Shannon's entropy to extract these factors automatically and then use them in an SVM to classify a more extensive data set. We then used dependency parsing and part of speech tagging to extract which nouns were tied to praising adjectives. We found that Chinese tourists are less concerned with hospitality and more with room quality than Western tourists. The latter were delighted by the staff behavior. We also found that Chinese tourists are concerned with the lack of a Chinese friendly environment, and Western customers are unsatisfied with dirty rooms or the smell of cigarettes.

@@

  Japan has been known historically for its hospitality being the highest grade. The spirit of Japanese hospitality is celebrated worldwide in a single Japanese word: \textit{Omotenashi}. With roots in Japanese history and tea ceremony, their hospitality is famous around the world \cite[][]{al2015characteristics}. Therefore it would stand to reason that tourists visiting Japan would have this hospitality as their first and foremost satisfaction factor. However, it is known that customers from different countries and cultures hold different expectations \cite[][]{engel1990}. Thus, it could be theorized that their satisfaction factors should be different. How will different cultures react and perceive hotels and their hospitality in this context? Our study attempts to bring light to this with two essential tourist populations that differ in culture to Japan: Chinese and Western tourists.

  In the last couple of decades, the Japanese economy has been more and more affected by an increase in inbound international tourism \cite[][]{jones2009}. There was a Year-on-Year Growth Rate of 19.3\% in 2017, with a total of \num[group-separator={,}]{28691073} inbound tourists that year \cite[][]{jnto2003-2019}. From this total, the tourist population was mostly Asian (86.14\%), and approximately a fourth of the total (25.63\%) came from China. Western countries, counting English-speaking countries and Europe, make for 11.4\% of the total, with a 7.23\% of the total being countries where English is the official or the de facto national language. The effect of Chinese tourists on international economies is increasing. From that, the number of researchers interested in this phenomenon has been increasing as well. \cite[][]{sun2017}. With these and other multicultural tourist populations, the tourist market is more and more diverse. Diversity in customers' cultural backgrounds means that their expectations when staying at a hotel will also be varied. Therefore, Hotel management needs to cater to these needs and expectations to increase customer satisfaction, maintain a good reputation, and generate positive word-of-mouth.

  However, many tourist behavior analyses have been performed with Western subjects. As such, a gap in knowledge and discussion existed until recent decades. Those studies that do include Asian populations in their analysis most commonly study Chinese tourist behavior \cite[e.g.][]{liu2019, chang2010, dongyang2015}. The few that compare Asian to Western tourist behavior \cite[e.g.][]{choi2000} are commonly survey or interview-based studies with small samples. These, while valid, can have their limitations. This gap in research creates a need for cross-cultural studies for the increasing Asian and Western tourist populations. It could be said that Westerners make for a smaller portion of the tourist population compared to Asians. However, according to \cite{choi2000}, Westerners are known as ``long-haul" customers, spending more than 45\% of their budget on hotel lodging. In comparison, their Asian counterparts only spend 25\% of their budget on hotels. Therefore, it is essential to study Asian and Western tourist populations, their differences, and contrast with the existing literature results.

@@

  In this study, we take advantage of the availability of enormous amounts of online reviews of Japanese hotels by both Mainland Chinese tourists posting in \textit{Ctrip} and Western English-speaking tourists populations posting in \textit{TripAdvisor}. With this data, we can confirm existing theories about their differences in behavior and explore the data to discover factors that could have been overlooked in the past. To do this, we use machine learning to automatically classify review sentences as positive or negative opinions of the hotel. We then perform a statistical extraction of the topics that concerns the customers of each population the most.

@@

  This study's objective is to determine the difference in factors driving satisfaction and dissatisfaction between Chinese and English-speaking tourists in the context of high-grade hospitality of Japanese hotels using text-mining techniques. We aim to contrast customer groups' satisfaction and dissatisfaction factors across several price ranges. We use machine learning to classify texts' sentiment and natural language processing to study commonly used word pairings. More importantly, we also intend to measure how hard and soft attributes influence customer groups' satisfaction and dissatisfaction. We define hard attributes as relating to physical aspects and environmental aspects, such as the hotel's facilities, the hotel's location, infrastructure, and real estate nearby. In contrast, soft attributes are the hotel's non-physical attributes related to services, staff, or management.

  Our proposal includes using large scale data from online hotel reviews in Chinese and English to study their differences in a statistical manner. In the past, survey-based studies have provided a theoretical background for a few specific tourist populations of a single culture or that travel with a single purpose. These studies' short scope often leads to difficulties in observing cultural and language differences in a single study.

@@

    The spirit of Japanese hospitality, or \textit{Omotenashi}, has roots in the countries history. However, to this day, it is regarded as the highest standard \cite[][]{ikeda2013omotenashi, al2015characteristics}. There is even a famous phrase in customer service in Japan: \textit{okyaku-sama wa kami-sama desu}, or translated ``The customer is god''. Some say that \textit{omotenashi} originated from the old Japanese art of the tea ceremony in the 16th century. However, other scholars found that its roots come from even earlier, in the form of formal banquets in the 7th-century \cite[][]{aishima2015origin}. The practice of high standards in hospitality has survived throughout the years. Today, it permeates all business practices in Japan, from the cheapest convenience stores to the most expensive ones. Manners, service, and respect towards the customer are taught to workers in their training. High standards are always followed as to not fall behind in the competition. In Japanese businesses, hotels included, staff members are trained to speak in \textit{sonkeigo}, or ``respectful language", one of the most formal of the Japanese formality syntaxes. They are also trained to bow with different depths depending on the situation, where a light bow could be used to say: ``Please, allow me to guide you". Deep bows are also used to apologize for any inconvenience the customer could have, followed by a very respectful apology. In fact, despite the word \textit{omotenashi} being translated directly as ``hospitality'', it includes both the concepts of hospitality and service \cite[][]{Kuboyama2020}. This hospitality culture permeates every kind of business with customer interaction in Japan. A simple convenience shop could express all of these hospitality and service standards, which are not exclusive to hotels.

    It stands to reason that this cultural aspect of hospitality would be a positive aspect that would be at the top of satisfaction for any customer. However, in many cases, other factors such as proximity to a convenience store, transport availability, or room quality might be more critical to a customer.  In this study, we cannot determine whether or not a hotel is practicing with the cultural standards of \textit{omotenashi} directly. Instead, we consider it as a cultural factor that influences all businesses in Japan. We then observe the customers' evaluations regarding service and hospitality factors in general, which can be compared to other places and business practices in the world. In summary, our study considers the influence of the cultural aspect of \textit{omotenashi} while analyzing the evaluations of service and hospitality factors that are universal to all hotels in any country.

@@

    Customer satisfaction in tourism has been analyzed since decades past, \cite{hunt1975} having defined customer satisfaction as the realization or overcoming of expectations towards the service. \cite{oliver1981} defined it as an emotional response to the provided services in retail and other contexts, and \cite{oh1996} reviewed the psychological processes of customer satisfaction for the hospitality industry. It is generally agreed upon that satisfaction and dissatisfaction stem from the individual expectations of the customer. As such, \cite{engel1990} states that each customer's background, therefore, influences satisfaction and dissatisfaction. Previous studies on the dimensions of culture that influence differences in expectations have been performed in the past \cite{donthu1998cultural}. Western and Chinese customers can then have very different satisfaction and dissatisfaction factors since they have different backgrounds and cultures. These varying backgrounds will lead to varying expectations of the hotel services, the experiences they want to have while staying at a hotel, and the level of comfort that they will have. These expectations will be there from the moment that they choose the hotel throughout their stay. In turn, these different expectations will determine the distinct factors of satisfaction and dissatisfaction for each kind of customer and the order in which they prioritize them.

@@

    However, in this study, we study not overall customer satisfaction but the satisfaction and dissatisfaction that stem from individual-specific expectations, be they conscious or unconscious. For example, suppose a customer has a conscious expectation of a comfortable bed and a wide shower, and it is realized during their visit. In that case, they will be satisfied with this matter. However, suppose that same customer with a conscious expectation of a comfortable bed experienced loud noises at night. In that case, they can be dissatisfied with a different aspect, regardless of the satisfaction towards the bed. Then, the same customer might have packed their toiletries, thinking that the amenities might not include those. They can then be pleasantly surprised with good quality amenities and toiletries, satisfying an unconscious expectation. This definition of satisfaction does not allow us to examine overall customer satisfaction. However, it will allow us to examine the factors that a hotel can revise individually and how a population perceives them as a whole. In our study, we consider the definitions by \cite{hunt1975} that satisfaction is a realization of an expectation, and posit that customers can have different expectations towards different service aspects. Therefore, in our study, we define satisfaction as the emotional response to the realization or overcoming of conscious or unconscious expectations towards an individual aspect or factor of a service. On the other hand, dissatisfaction is the emotional response to the lack of a realization or under-performance of these conscious or unconscious expectations towards specific service aspects.

    Studies on customer satisfaction \cite[e.g.][]{truong2009, romao2014, wu2009} commonly use the Likert scale \cite[][]{likert1932technique} (e.g. 1 to 5 scale from strongly dissatisfied to strongly satisfied) to perform statistical analysis of which factors relate most to satisfaction on the same dimension as dissatisfaction \cite[e.g.][]{chan201518, choi2000}. The Likert scale's use leads to correlation analyses where one factor can lead to satisfaction, implying that the lack of it can lead to dissatisfaction. However, a binary distinction (satisfied or dissatisfied) could allow us to analyze the factors that correlate to satisfaction and explore factors that are solely linked to dissatisfaction. There are fewer examples of this approach, but studies have done this in the past \cite[e.g.][]{zhou2014}. This method can indeed decrease the extent to which we can analyze degrees of satisfaction or dissatisfaction. However, it has the benefit that it can be applied to a large sample of text data via automatic sentiment detection techniques using artificial intelligence.

    Previous research has also focused more on soft attributes, with little focus on hard attributes, like location or infrastructure, mostly focusing only on facilities \cite[e.g.][]{shanka2004, choi2001}. However, hard factors, which are uncontrollable by the hotel staff, can play a part in the customers' choice behavior and satisfaction. Examples of these factors include the hotel's surroundings, location, language immersion of the country as a whole, or touristic destinations, and the hotel's integration with tours available nearby, among other factors.

@@

@@

    % Asians vs. Western behavior
    In the past, social science and tourism studies focused extensively on Western tourist behavior in other countries. Recently, however, with the rise of Chinese outbound tourism, both academic researchers and businesses have decided to study Chinese tourist behavior. Explaining this increase, \cite{sun2017} analyzed the number of studies related to Chinese tourists from 2001 to 2012 and found a steady increase until 2007, followed by the rapid growth of Chinese tourism studies. This increase in Chinese tourist behavior research resulted in several studies focusing on only the behavior of this subset of tourists. To this day, studies and analyses specifically comparing Asian and Western tourists are scarce, and even less the number of studies explicitly comparing Chinese and Western tourists. One example is a study by \cite{choi2000}, who found that Western tourists visiting Hong Kong are satisfied more with room quality, while Asians are satisfied with the value for money. Another study by \cite{bauer1993changing} found that Westerners prefer hotel health facilities. At the same time, Asian tourists were more inclined to enjoy the Karaoke facilities of hotels. Both groups tend to have high expectations for the overall facilities. Another study done by \cite{kim2000} found that American tourists were found to be individualistic and motivated by novelty. In contrast, Japanese tourists were collectivist and motivated by prestige and family, with an escape from routine and increased knowledge as a common motivator.

    One thing to note with the above Asian vs. Western analyses is that they were performed before 2000 and that they are not Chinese specific but study Asian people in general. Meanwhile, the current Chinese economy boom is increasing the influx of tourists of this nation. The resulting increase in marketing and the creation of guided tours for Chinese tourists could have created a difference in tourists' perceptions and expectations. In turn, if we follow the definition of satisfaction by \cite{hunt1975}, that change in expectations could have influenced their satisfaction factors when traveling. Another note is that these studies were performed with questionnaires in places where it would be easy to locate tourists, i.e., airports. However, our study of online reviews takes the data that the hotel customers uploaded themselves. This data makes the analysis unique in exploring their behavior compared with Western tourists via factors that are not considered in most other studies. Furthermore, our study is unique in observing the customers in the specific environment of high-level hospitality in Japan.

@@

    % Universal behavior
    Other studies have gone further and studied people from many countries in their samples and performed a more universal and holistic (not cross-culture) analysis. \cite{choi2001} analyzed hotel guest satisfaction determinants in Hong Kong with surveys in English, Chinese and Japanese translations, with people from many countries in their sample. \cite{choi2001} found that staff service quality, room quality, and value for money were the top satisfaction determinants. As another example, \cite{Uzama2012} produced a typology for foreigners coming to Japan for tourism, without making distinctions for their culture, but their motivation in traveling in Japan. In another study, \cite{zhou2014} analyzed hotel satisfaction using English and Mandarin online reviews from guests staying in Hangzhou, China coming from many different countries. The general satisfaction score was noticed to be different in those countries. However, a more in-depth cross-cultural analysis of the satisfaction factors was not performed. As a result of their research, \cite{zhou2014} thus found that customers are universally satisfied by welcome extras, dining environments, and special food services.

@@

    % Chinese behavior
    Regarding outbound Chinese tourists, academic studies about Chinese tourists have increased \cite[][]{sun2017}. Different researchers have found that Chinese tourist populations have several specific attributes. According to \cite{ryan2001} and their study of Chinese tourists in New Zealand, Chinese tourists prefer nature, cleanliness, and scenery in contrast to experiences and activities. \cite{dongyang2015} studied Chinese tourists in the Kansai region of Japan and found that Chinese tourists are satisfied mostly with exploring the food culture of their destination, cleanliness, and staff. Studying Chinese tourists in Vietnam, \cite{truong2009} found that Chinese tourists are highly concerned with value for money. According to \cite{liu2019}, Chinese tourists tend to have harsher criticism compared with other international tourists. Moreover, as stated by \cite{gao2017chinese}, who analyzed different generations of Chinese tourists and their connection to nature while traveling, Chinese tourists prefer nature overall. However, the younger generations seem to do so less than their older counterparts.

@@

    % Reviewer comparison table
    Undoubtedly previous literature has examples of other cross-culture studies of tourist behavior and to further highlight our study and its merits. A contrast is shown in Table \ref{tab:lit-rev}. This table shows that older studies were conducted with surveys and had a different study topic. These are changes in demand \cite[][]{bauer1993changing}, tourist motivation \cite[][]{kim2000}, and closer to our study, satisfaction levels \cite[][]{choi2000}. However, our study topic is not the levels of satisfaction but the factors that drive it and dissatisfaction, which is overlooked in most studies. Newer studies with larger samples and similar methodologies have emerged, although two of these study restaurants instead of hotels \cite[][]{JIA2020104071, HUANG2017117}. One important difference is the geographical focus of their studies. While \cite{FRANCESCO201924} , \cite{JIA2020104071} and \cite{HUANG2017117} have a multi-national focus, we instead focus on Japan. The focus on Japan is important because of its top rank in hospitality across all types of businesses. This raises the question: in such an environment, will the customers be universally satisfied with this factor, or will they have differing views within their cultures? Our study brings light to the changes, or lack thereof, in different touristic environments where an attribute can be considered excellent. The number of samples in other text-mining studies is also smaller than ours in comparison. Apart from that, every study has a different text mining method.

@@

    % Machine Learning
    The algorithm used for sentiment analysis in our study is called a Support Vector Machine. It is a form of supervised machine learning used for binary classification. This means a sample of labeled training data is given to the algorithm to detect patterns in the data and use those patterns to establish a method for classifying other unlabeled data automatically. Machine learning is a general term used for algorithms that, when given data, will automatically use that data to "learn" from its patterns and apply them for improving upon a task. Learning machines can be supervised, as in our study, where the algorithm has manually labeled data to know the correct task result template. Machine learning can also be unsupervised, where without any pre-labeled data. In this latter case, the machine will analyze the structure and patterns of the data and perform a task based on its conclusions. Our study calls for a supervised machine since text analysis can be intricate. Many patterns might occur, but we are only interested in satisfaction and dissatisfaction labels. Consequently, we teach the machine through previously labeled text samples.

    Machine learning and data mining are two fields with a significant overlap since they can use each other's methods to achieve the task at hand. Machine learning methods focus on predicting new data based on known properties and patterns of the given data. Data mining, on the other hand, is discovering new information and new properties of the data. Our machine learning approach will learn the sentiment patterns of our sample texts showing satisfaction and dissatisfaction and using these to label the rest of the data. We are not exploring new patterns in the sentiment data. However, we are using sentiment predictions for knowledge discovery in our database. Thus our study is a data mining experiment based on machine learning.

    % Data exploration
    Because the methodology for finding patterns in the data is automatic and statistical, it is both reliable and unpredictable. Reliable in that the algorithm will find a pattern by its nature. Unpredictable in that since it has no intervention from the researchers in making questionnaires, it can result in anything that the researchers could expect. These qualities determine why, much like actual mining, data mining is mostly exploratory. One can never be sure that one will find a specific something. However, we can make predictions and estimates about finding knowledge and what kind of knowledge we can uncover. The exploration of large opinion datasets with these methods is essential. The reason being we can discover knowledge that could be missed by looking at a localized sample rather than a holistic view of every users' opinion. In other words, a machine algorithm can find the needles in a haystack that we did not know were there from taking small bundles of hay at a time.
